### 2017-08-20 src/4_OnlineLearning.tex
ultimos comentarios

Supervised learning consists in finding a learning function $f: X \rightarrow Y$
which models a set of examples, called training set $S$, which have been drawn
randomly and independently according to a unknown joint distribution function
$p(x,y)$ on $X \times Y$:

$$
S = \{ (x_k,y_k)\in X\times Y : k=1,...,n \}
$$

\noindent where $X \subseteq \mathbb{R}^m$ and $Y = \mathbb{R}$ in case of
regression problems and $Y = \{1,-1\}$  if it is a classification problem.

A learning algorithm $\mathcal{A}$ takes as input a data set $S \in
\mathscr{T}=\mathscr{P}(X\times Y)$ and selects from $\mathcal{H}$ a function
$f$ such that $f(x)\approx y $ in a predictive way:

\begin{eqnarray*}
\mathcal{A}: \mathscr{T} &\rightarrow & \mathcal{H} \\
S &\rightarrow &\mathcal{A}(S) = f
\end{eqnarray*}

\noindent where $\mathcal{H}$ is called the {\em hypothesis space}, i.e. the space
of functions that the algorithm is allowed to search. The selection of
$f$ is based on the minimisation of the expected error of the loss
function $V(f(x),y): Y \times Y$ defined as:

\begin{eqnarray}
\label{eq:lossfunction}
 V & \rightarrow & \mathbb{R}^+ \\
  (f(x), y) &\rightarrow & V(f(x),y)
\end{eqnarray}

\noindent where $V(f(x),y)$ denote the price paid for mistakes, $f:X=\R^m\to Y$ and
$y=f(x)\in\R$. Therefore, $V(f(x),y)=0$ if $\;f(x)=y$.

@@

\begin{equation}
\label{eq:expetedrisk}
E[V(f(x),y)] = \int_{X\times Y} V(f(x),y)\;dp(x,y)\,,
\end{equation}

For regression, the most common loss function is square loss or L2 loss function:
\begin{equation}
\label{eq:l2loss}
V(f(x),y) = (f(x)-y)^2
\end{equation}
\noindent another option is the L1 loss
\begin{equation}
\label{eq:l1loss}
V(f(x),y) = |f(x)-y| \, .
\end{equation}
\noindent the choice of loss function here gives rise to several well-known
learning algorithms such as regularised least squares and support vector
machines. %verificar esto

@@

\begin{equation*}
\hat{f} = \argmin_{f \in \mathcal{H}} R_{\text{emp}}[f] 
\end{equation*}

@@

\begin{equation}
\frac{1}{n} \sum_{i=1}^n V(f(x_i),y_i) \xrightarrow{n \rightarrow \infty}  E[V(f(x),y)]
\end{equation}

\subsection{Learning algorithms}
In all learning algorithms that are trained from example data, there is a
tradeoff between three factors \cite{dietterich2003}:
\begin{description}
\item[Complexity or capacity of the hypothesis class] is defined in terms of the
Vapnik-Chervonenkis (VC) dimension, which corresponds to the number of training
points that can be classified exactly by the hypothesis space. More formally,
the VC dimension of the hypothesis space $\mathcal{H}$ defined over instance
space $X$ is the size of the largest finite subset of $X$ shattered by
$\mathcal{H}$. The dataset $S$ is shattered by hypothesis space $\mathcal{H}$ if
and only if for every dichotomy of $S$ there exists some hypothesis in
$\mathcal{H}$ consistent with this dichotomy. A dichotomy of a set $S$ is a
partition of $S$ into two disjoint subsets \cite{vapnik2013nature}.

@@

\begin{align}
\label{eq:bvtrade}
\mathrm{E}\Big[\big(y - \hat{f}(x)\big)^2\Big]
 & = \mathrm{Bias}(\hat{f}(x))^2 + \mathrm{Var}(\hat{f}(x)) + \sigma^2
\end{align}
\noindent where:
\begin{align}
 \mathrm{Bias}(\hat{f}(x)) &= \mathrm{E}\big[\hat{f}(x)\big] - f(x) \label{eq:biastrade}\\
 \mathrm{Var}(\hat{f}(x)) &= \mathrm{E}\Big[ \big( \hat{f}(x) - \mathrm{E}[\hat{f}(x)] \big)^2 \Big]  \label{eq:variancetrade}
\end{align}

@@

Tikhonov introduced a regularization which ensures well-posedness and
generalisation of ERM, i.e prevents overfit, by constraining the hypothesis
space $\mathcal{H}$ usually called regularised ERM or Tikhonov regularisation.

%Tikhonov regularisation minimised over the hypothesis space $\mathcal{H}$ for a
%fixed positive parameter $\lambda$ the following:
Tikhonov regularisation considers a functional of the form:

>>>>

%Supervised learning consists in finding a learning function $f: X \rightarrow Y$
%which models a set of examples, called training set $S$, which have been drawn
%randomly and independently according to a unknown joint distribution function
%$p(x,y)$ on $X \times Y$:
%
%
%$$
%S = \{ (x_k,y_k)\in X\times Y : k=1,...,n \}
%$$
%
%\noindent where $X \subseteq \mathbb{R}^m$ and $Y = \mathbb{R}$ in case of
%regression problems and $Y = \{1,-1\}$  if it is a classification problem. 
%
%
%A learning algorithm $\mathcal{A}$ takes as input a data set $S \in
%\mathscr{T}=\mathscr{P}(X\times Y)$ and selects from $\mathscr{H}$ a function
%$f$ such that $f(\mathbf{x})\approx y $ in a predictive way:
%
%\begin{eqnarray*}
%\mathcal{A}: \mathscr{T} &\rightarrow & \mathscr{H} \\
%S &\rightarrow &\mathcal{A}(S) = f
%\end{eqnarray*}
%
%\noindent where $\mathscr{H}$ is called the {\em hypothesis space}, i.e. the space
%of functions that the algorithm is allowed to search.

%------------------------DRAFT PROFE -------------------------------
The basic setting for supervised learning is a {\em data set\/} $X$, 
and an  {\em outcome set\/} $Y$.
For our purposes $X$ will be $\R^m$, $m\in\N$, and $Y$ either $\R$
in the case of regression problems, or $\{-1,1\}$ in the case of
classification problems.
In addition we have a plurality of {\em training sets\/}
$$
S=\bigg\{ (\mathbf{x}_k,y_k)\in X\times Y \mid k=1,\dots,n \bigg\}
\subseteq X\times Y\,,
$$
where the members of $S$ have been drawn randomly and independently
from $X\times Y$ according to an {\em unknown\/} joint distribution
function $p(\mathbf{x},y)$ on $X\times Y$.
We gather all these training sets in a subset $\mathscr{T}$ of
$\mathscr{P}(X\times Y)$.

In addition, there is a {\em learning algorithm\/} $\mathcal{A}$ that
associates to every data set one and only one learning function
$f\in\mathscr{H}$.
Thus $\mathcal{A}$ can be considered as a function:
$$
\mathcal{A}:\mathscr{T}\to\mathscr{H}\,,\qquad
S\mapsto\mathcal{A}(S)=f\quad\forall S\in\mathscr{T}\,.
$$

%------------------------FIN DRAFT PROFE -------------------------------
{\em Supervised learning\/} consists then in finding a {\em learning function\/}
$f:X\to Y$ that minimisr the expected error of the loss function $V(f(\mathbf{x}),y): Y
\times Y$ defined as:

\begin{eqnarray*}
\label{eq:lossfunction}
 V & \rightarrow & \mathbb{R}^+ \\
  (f(\mathbf{x}), y) &\rightarrow & V(f(\mathbf{x}),y)
\end{eqnarray*}

\noindent where $V(f(\mathbf{x}),y)$ denote the price paid for mistakes, $f:X=\R^m\to Y$
and $y=f(\mathbf{x})\in\R$. Therefore, $V(f(\mathbf{x}),y)=0$ if $\;f(\mathbf{x})=y$.

@@

\begin{equation}
\label{eq:expetedrisk}
%E[V(f(\mathbf{x}),y)] = \int_{X\times Y} V(f(\mathbf{x}),y)\;dp(x,y)\,,
E\big[ V( f(\cdot),\cdot) \big]
= \int_{X\times Y} V\big( f(\mathbf{x},y \big)\,dp(\mathbf{x},y)\,.
\end{equation}

For regression, the most common loss function is square loss or L2 loss function:
\begin{equation}
\label{eq:l2loss}
V(f(\mathbf{x}),y) = (f(\mathbf{x})-y)^2
\end{equation}
\noindent another option is the L1 loss
\begin{equation}
\label{eq:l1loss}
V(f(\mathbf{x}),y) = |f(\mathbf{x})-y| \, .
\end{equation}
\noindent the choice of loss function here gives rise to several well-known
learning algorithms such as regularised least squares and support vector
machines. %verificar esto

@@

\begin{equation*}
\hat{f} = \argmin_{f \in \mathscr{H}} R_{\text{emp}}[f] 
\end{equation*}

@@

\begin{equation}
\frac{1}{n} \sum_{i=1}^n V(f(x_i),y_i) \xrightarrow{n \rightarrow \infty}  E[V(f(\mathbf{x}),y)]
\end{equation}

\subsection{Learning algorithms}
In all learning algorithms that are trained from example data, there is a
tradeoff between three factors \cite{dietterich2003}:
\begin{description}
\item[Complexity or capacity of the hypothesis class] is defined in terms of the
Vapnik-Chervonenkis (VC) dimension, which corresponds to the number of training
points that can be classified exactly by the hypothesis space. More formally,
the VC dimension of the hypothesis space $\mathscr{H}$ defined over instance
space $X$ is the size of the largest finite subset of $X$ shattered by
$\mathscr{H}$. The dataset $S$ is shattered by hypothesis space $\mathscr{H}$ if
and only if for every dichotomy of $S$ there exists some hypothesis in
$\mathscr{H}$ consistent with this dichotomy. A dichotomy of a set $S$ is a
partition of $S$ into two disjoint subsets \cite{vapnik2013nature}.

@@

\begin{align}
\label{eq:bvtrade}
\mathrm{E}\Big[\big(y - \hat{f}(\mathbf{x})\big)^2\Big]
 & = \mathrm{Bias}(\hat{f}(\mathbf{x}))^2 + \mathrm{Var}(\hat{f}(\mathbf{x})) + \sigma^2
\end{align}
\noindent where:
\begin{align}
 \mathrm{Bias}(\hat{f}(\mathbf{x})) &= \mathrm{E}\big[\hat{f}(\mathbf{x})\big] - f(\mathbf{x}) \label{eq:biastrade}\\
 \mathrm{Var}(\hat{f}(\mathbf{x})) &= \mathrm{E}\Big[ \big( \hat{f}(\mathbf{x}) - \mathrm{E}[\hat{f}(\mathbf{x})] \big)^2 \Big]  \label{eq:variancetrade}
\end{align}

@@

Tikhonov introduced a regularization which ensures well-posedness and
generalisation of ERM, i.e prevents overfit, by constraining the hypothesis
space $\mathscr{H}$ usually called regularised ERM or Tikhonov regularisation.

%Tikhonov regularisation minimised over the hypothesis space $\mathscr{H}$ for a
%fixed positive parameter $\lambda$ the following:
Tikhonov regularisation considers a functional of the form:
